---
title: "Cryptocurrencies"
author: "Javier Gonzalez"
date: "3 de julio de 2018"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r initialization, echo = FALSE, message=FALSE}
require(plotly)
require(dplyr)
btc = read.csv("data/BTC.csv", dec=",", sep=";")
btc$Fecha = as.Date(btc$Fecha, format="%d/%m/%Y")
dfg <- btc[order(btc$Fecha),] 

calculateSegment <- function(data, interval, selected) {
    dateSelect = as.Date(selected, origin=lubridate::origin)
    df <- data %>% filter(Fecha <= dateSelect , Fecha >= dateSelect - interval)
    
    model <- lm(End ~ Fecha, data=df)
    
    y1 <- model$coefficients[1] + model$coefficients[2] * as.numeric(df[1,"Fecha"])
    y2 <- model$coefficients[1] + model$coefficients[2] * as.numeric(df[nrow(df),"Fecha"])
    X <- c(df[1,"Fecha"], df[nrow(df),"Fecha"])
    Y <- c(y1, y2)
    
    df <- as.data.frame(cbind(x=X, y=Y))
    df$x = as.Date(df$x, origin=lubridate:::origin)

    return(df)
}

```

## R Markdown

This is a little application to analyze cryptocurrencies evolution using quantitative analysis

For this demo:

- Sample data are stored in a csv file but the original idea use an external database with update prices
- Only _Mobile Means_ for four intervals are implemented
- Vertical Red line set the current date/cotization

## Candlestick sample

This is a sample of data using candlestick chart style.

You can zooming in to get detailed info

```{r plot1}
 p <- plot_ly(dfg, x = ~Fecha, type = 'candlestick', open = ~Beg, close = ~End, high = ~High, low = ~Low)
 p <- layout(p, xaxis = list(rangeslider = list(visible = F)))
 p
```

## Median mobile sample

- Orange line is the MM for 1 week
- Green line is the MM for 1 month

```{r lineal, echo = FALSE}
    f <- "2018-01-05"
    df <- dfg %>% filter(Fecha >= "2017-10-01" , Fecha <= "2018-03-01")
    p <- plot_ly(df, x = ~Fecha, y = ~End, type = 'scatter', mode = 'markers + lines')
    p <- layout(p, shapes=list(type="line", fillcolor="red",line=list(color="red")
                                          ,opacity=1
                                          ,x0=f, x1="2018-01-05", xref="x"
                                          ,y0=0, y1=1, yref="paper")
         )
    segment <- calculateSegment(df, 7, f)
    p <- add_trace(p, x=~x, y=~y, data=segment, mode="lines", showlegend = F)
    segment <- calculateSegment(df, 30, f)
    p <- add_trace(p, x=~x, y=~y, data=segment, mode="lines", showlegend = F)

   p
```

## Web page

https://grandez.shinyapps.io/CTC1/

It's only work on browser not in RStudio

```{r sc}
 knitr::include_app("https://grandez.shinyapps.io/CTC1/", height="800px")
```

